---
title: "Live Demonstration"
author: "Ronan Machin"
date: "17/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(reactable)
library(crosstalk)
library(kableExtra)
```

## Formatting Tables

Below is a handy package for formatting tables (kableExtra). It works intuitively with the tidyverse syntax using a data.frame object.

```{r cars, echo=F}
head(mtcars) %>%
  kbl() %>%
  kable_styling(full_width = FALSE)
```

## Interative Plots

Below I have combined three packages to demonstrate interactivity within html reports or dashboards. They are Plotly, Reactable & crosstalk.

Plotly is a package for interactive charts, Reactable for reactive tables and crosstalk allows user interaction to be mirrored in the data behind both objects.


```{r pressure, echo=FALSE}
small_df = mtcars %>%
  mutate(Model = rownames(mtcars)) %>%
  select(Model, mpg, cyl, drat, wt) %>%
  na.omit()

rownames(small_df)=NULL

pen_df = SharedData$new(small_df)

plotly_graphic = plot_ly(pen_df,
                         x = ~wt,
                         y = ~mpg,
                         color = ~cyl, 
                         text = ~Model,
                         type = "scatter",
                         mode = "markers") %>%
  #add_markers() %>%
  highlight(on = "plotly_selected",
            off = "plotly_doubleclick")#,
  #          persistent = FALSE)

plotly_graphic

reactable_table = reactable(pen_df, 
                            columns = list(
                              Model = colDef("Model"),
                              mpg = colDef("Miles per Gallon"),
                              drat = colDef("DRAT"),
                              wt = colDef("Weight")))


reactable_table
```

